\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Oussema Hidri}

\section{Work experience}

\begin{eventlist}

\eventbegin{Software Developer Intern}
         {Domesting - A Coruna, Spain}

\begin{cvitems}
\item { Used \href{https://www.meteor.com/}{Meteor}, \href{https://www.mongodb.com}{MongoDB}, \href{https://angularjs.org/}{AngularJs} and \href{https://ionicframework.com/}{Ionic}.
}    \item { Implemented and improved ERP of existing cleaning companies and hotels.
}    \item { Addd reports with \href{http://www.chartjs.org/}{chartJs} for various information.
}    \item { Used \href{https://www.atlassian.com/software/jira}{JIRA}, \href{https://bitbucket.org/product}{bitbucket} and \href{https://slack.com}{Slack} as the basis tools for managing the workflow of the company.
     \item {Had regular meetings to explain new ideas and features.}
}\end{cvitems}

\eventend{Jul. 2017 -- Sep. 2017}

\eventbegin{Hybrid Mobile Developer Intern}
     {Proxym Group - Sousse, Tunisia}

    \begin{cvitems}
    \item {Used \href{https://www.ibm.com/mobile/}{IBM Mobile First}, \href{https://angularjs.org/}{AngularJs}, \href{https://cordova.apache.org/}{Apache Cordova} and \href{https://ionicframework.com/}{Ionic}}.
    \item{Implemented the process of automatically fetch news from different sources and save them in a separate server.}
    \item{Implemented the possibility of locally save a list of different news.}
    \item{Implemented a section to display weather \href{https://openweathermap.org}{openweather} of the current user’s location.}
    \end{cvitems}

\eventend{Jul. 2016 -- Aug. 2016}

\end{eventlist}

\section{Personal Projects}

\begin{eventlist}

    \eventbegin{Manipulating TensorFlow Models}{}
    
    \begin{cvitems}
    \item {Used \href{https://www.tensorflow.org}{TensorFlow}, \href{https://www.tensorflow.org/get_started/summaries_and_tensorboard}{TensorBoard}, \href{https://www.python.org}{Python}, and \href{https://developer.android.com/index.html}{Android}.}
    \item {Used pre-trained models (\href{https://github.com/affinelayer/pix2pix-tensorflow}{pix2pix}) to freeze and optimize for inference with Python to be able to deploy the models in an Android app.}
    \end{cvitems}

\eventend{Oct. 2017}



\eventbegin{Handling \& Analyzing a Social Network Data}
    {}

    \begin{cvitems}
        \item {Used \href{http://snap.stanford.edu/data/egonets-Facebook.html}{snap} data of Facebook users and \href{http://graphstream-project.org/}{graphstream} for the visualization.}
        \item {Implemented a Java application using Graph Data Structure to predict smartphone buying for a social network.}
    \end{cvitems}
\eventend{Mid 2016}


\eventbegin{Knock Alarm Clock}
    {}

    \begin{cvitems}
    \item {Used \href{https://www.arduino.cc}{Arduino} uno, LCD and \href{https://www.digi.com/xbee}{Xbee} modules.}
    \item {Implemented an alarm clock that turns off only with an entered knock pattern.}
    \item {Implemented the possibility to communicate with the microcontroller wirelessly through xbees.}
    \end{cvitems}
    
\eventend{Summer 2015}


\eventbegin{Website for local Coffee Shops}
    {}
        
    \begin{cvitems}
    \item {Used \href{http://php.net}{php}, \href{https://www.javascript.com}{javascript} and \href{http://reel360.org/reel}{reel360}.}
    \item {Implemented a website that displays different virtual tours of coffee shops and list their services.}
    \item {Created a little framework with php and an admin dashboard with javascript to manage the website.}
    \end{cvitems}
\eventend{Mid 2014}


\end{eventlist}

\personal
    []
    {Turkie Street Sahloul 1, 4054 Sousse, Tunisia } 
    {+216 53160059}
    {d.oussema.d@gmail.com}
    {dmidma}
    {oussema-hidri}

\section{Education}

\begin{yearlist}

\item{Computer Science \& Software Engineer Student}
     {Sep. 2015 -- Present}
     {}
     {Higher Institute of Applied Sciences and Technology Sousse}
     {http://www.issatso.rnu.tn/fo/index.php}

\end{yearlist}


\section{Online Courses}


\begin{yearlist}

\item{Machine Learning}
     {Dec. 2017}
     {}
     {Stanford Univ. on Coursera}
     {}


\item
    {Big Data Modeling and Management Systems}
    {November 2016}
    {}
    {Univ. of California, San Diego on Coursera}
    {https://www.coursera.org/account/accomplishments/records/XKQAA4TAMNPT}



\item
    {Java Programming: Object-Oriented Design of Data Structures, a 5-course specialization}
    {May 2016}
    {}
    {University of California, San Diego on Coursera}
    {https://www.coursera.org/account/accomplishments/specialization/TPG9YUL829L2}

\item
    {Game Theory I \& II}
    {2015}
    {}
    {Stanford Univ. \& Univ. of British Columbia on Coursera}
    {}

\item
    {Introduction to Computer Science - CS50}
    {2015}
    {}
    {HarvardX - edx}
    {https://courses.edx.org/certificates/864f3370efea44d1a1b4f31b9659e734}

\end{yearlist}


\section{Communication skills}

\begin{factlist}
\item{Arabic}{Native speaker}
\item{English}{Oral: good -- Written: good}
\item{French}{Oral: good -- Written: good}
\end{factlist}

\section{Software skills}

\begin{factlist}

\item{Good level}
     {C, PHP, HTML, CSS, Java, git, shell,
      JavaScript, Linux, MySQL, MongoDB, vim, tmux}

\item{Intermediate}
     {Machine Learning, TensorFlow, Android, Arduino, Photoshop}

\item{Basic level}
     {Python, c++, \LaTeX}

\end{factlist}

\end{document}
